%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page One Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column 20s contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{ragged2e}
 
\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Sadashay}{Kanungo}{ 
+91 8178849236 \: | \: \href{mailto:sadashay01@gmail.com}{\bf sadashay01@gmail.com} \: | \: LinkedIn  \href{https://www.linkedin.com/in/sadashay-kanungo/}{\bf @sadashay-kanungo} \: | \: Github \href{https://github.com/SadashayKanungo}{\bf @SadashayKanungo}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     EDUCATION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Birla Institute of Technology and Science, Pilani, K K Birla Goa Campus \hfill Jun 2024}
\newline 
\descript{B.E. Computer Science With M.Sc. Economics \hfill CGPA: 8.23}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     EXPERIENCE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Nykaa E-Retail Ltd.}
\runsubsectionside{Technology Intern}{Jan 2024 – Present}
\location{Python \textbullet{} SQL \hfill Bangalore, IND}
\begin{tightemize}

\item Currently developing a \textbf{prediction model} for \textbf{forecasting demand} of new products for optimal procurement before launch.

\item Developed a \textbf{prediction model} for approximating improvements in \textbf{Net Promoter Score} with varying customer experience.

\item Compiled a comprehensive report on \textbf{Net Promoter Score} after analysing customer feedback data; which was used by the \textbf{Executive Board} to assess performance and formulate business targets.

\end{tightemize}
\sectionsep

\runsubsection{Amazon Inc.}
\runsubsectionside{Software Development Engineer Intern}{Jul 2023 – Dec 2023}
\location{AWS \textbullet{} Apache Spark \textbullet{} Scala \textbullet{} Java \textbullet{} Typescript \textbullet{} SQL \hfill Bangalore, IND}
\begin{tightemize}

\item Contributed to \textbf{architectural redesign and migration} of Sherlock (Financial Reconciliation framework) resulting in \textbf{3 times faster on-boardings} for customers with \textbf{reduced engineering effort}.\:\: (Stack: {AWS EMR}, {S3}, {Glue}, {Athena}, {CloudFormation})

\item Delivered \textbf{project-critical design changes} for Watson (Reconciliation Monitoring and Reporting framework) establishing its compatibility with Sherlock's new architecture.\:\: (Stack: {AWS Lambda}, {Step Function}, {CloudWatch}, {AWS CDK})

\item Integrated \textbf{Tickety API service} into Watson, resulting in simplification of design, \textbf{deprecation of legacy infrastructure} and yielding \textbf{annual savings of over 1000 USD in hardware cost}.\:\: (Stack: {AWS Lambda}, {AWS SAM}, {Dagger}, {Mockito})

\item Built and automated \textbf{AWS Quicksight Dashboards} for publishing Reconciliation reports which were earlier being shared as Excel files. This transition resulted in an \textbf{elevated user experience}, new features like \textbf{access control} and \textbf{data visualization}.

\end{tightemize}
\sectionsep

\runsubsection{Blue Rocket LLC.}
\runsubsectionside{Freelance Developer \,|\,
\href{https://sadashaykanungo.github.io/Resume/BlueRocketLOR.pdf}{\underline{LOR} \small\nearrow}
\space
\href{https://elephant.ai}{\underline{LINK} \small\nearrow}}{April 2023 – May 2023}
\location{OpenAI-API \textbullet{} Flask \textbullet{} MongoDB \textbullet{} React.js \textbullet{} Stripe-API \hfill Remote}
\begin{tightemize}
\item Designed, developed and delivered \textbf{Elephant.ai}, a feature-complete \textbf{No-Code Platform} enabling business owners to create and deploy \textbf{Custom GPT-powered Chatbots} trained on their website's content to resolve queries and boost engagement.
\item Elephant.ai (v1.0) was adopted by \textbf{1,500+ paying customers} in a span of 9 months before being superseded by  v2.0
\end{tightemize}
\sectionsep

\runsubsection{Google Summer of Code}
\runsubsectionside{Contributor \,|\,
\href{https://medium.com/scorelab/search?q=sadashay+kanungo}
{\underline{BLOG} \small\nearrow}
\space \href{https://summerofcode.withgoogle.com/programs/2022/projects/2PHsoS0l}{\underline{LINK} \small\nearrow}}{June 2022 – Sep 2022}
\location{Typescript \textbullet{} Node.js \textbullet{} Solidity \textbullet{} Ethereum \textbullet{} IPFS \textbullet{} Mocha \textbullet{} Docusaurus \hfill Remote}
\begin{tightemize}
\item Conceptualized, designed and developed \textbf{NFT-Toolbox}, an \textbf{NPM package} providing \textbf{simplistic APIs for all NFT related tasks} viz., \textbf{Batch Image Generation} from layers, \textbf{IPFS Storage} on multiple providers, \textbf{Smart Contract} deployment and interactions.
\item NFT Toolbox was introduced as a new project in \textbf{GSoC 2022}. It has been selected for the programme every year since then and continues to be developed by the open source community.
\end{tightemize}
\sectionsep

\runsubsection{W3Dev Pvt. Ltd.}
\runsubsectionside{Blockchain Development Intern}{Dec 2021 – Jan 2022}
\location{Solidity \textbullet{} Ethereum \textbullet{} TypeScript \textbullet{} GraphQL \textbullet{} GraphNetwork \hfill Remote}
\begin{tightemize}

\item Developed and deployed \textbf{Smart Contracts} for an \textbf{NFT Marketplace} application supporting NFT minting, sales and auctions.

\item Created a subgraph on \textbf{GraphNetwork} and designed it's \textbf{GraphQL Schema} for storing NFT Marketplace's \textbf{data parsed from on-chain events}; resulting in \textbf{elimination of gas costs} for retrieving data, \textbf{faster queries} and \textbf{lower latency} on the front-end.

\end{tightemize}
\sectionsep

\runsubsection{Platifi Solutions Ltd.}
\runsubsectionside{Software Development Intern}{May 2021 – July 2021}
\location{MongoDB \textbullet{} Express.js \textbullet{} React.js \textbullet{} Node.js \textbullet{} ElasticSearch \hfill Remote}
\begin{tightemize}
\item Led team of 6 interns to design and develop a \textbf{Covid-Tracker} application with \textbf{MERN stack}.
\item Developed a POC showcasing \textbf{Search Autocomplete} feature implemented using \textbf{ElasticSearch}.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     PROJECTS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Projects}



% \runsubsection{Makeup Verification System}
% \descript{| Blockchain \hfill 
% \href{https://github.com/SadashayKanungo/MakeupVerificationSystem}{CODE \small\nearrow}
% \space\space
% \href{https://makeup-system.onrender.com/}{LINK \small\nearrow}}
% \location{Python \textbullet{} FastAPI \hfill Sep 2022 – Dec 2022}
% \begin{tightemize}
% \item A robust system for {\bf verification of Medical documents} submitted by students to avail Makeups for missed examinations.
% \item Implemented {\bf Blockchain for scratch} with {\bf Python} and {\bf FastAPI}.
% \end{tightemize}
% \sectionsep

% \runsubsection{Chat App}
% \descript{| Web Sockets \hfill 
% \href{https://github.com/SadashayKanungo/ChatApp-NodeJSCourse}{CODE \small\nearrow}
% \space\space
% \href{https://kanungo-chat.onrender.com/}{LINK \small\nearrow}}
% \location{Node.js \textbullet{} Socket.io \hfill Sep 2022 – Dec 2022}
% \begin{tightemize}
% \item A Simplistic Live \textbf{Chatting Application}, with support for \textbf{multiple concurrent chat rooms}.
% \item Developed with Socket.io and Node.js.
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     SKILLS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}
\runsubsection{Languages}
\descript{\large :\: {TypeScript,\: JavaScript,\: Java,\: Python,\: C++,\: SQL,\: Solidity,\: Scala,\: Kotlin}}

\runsubsection{Frameworks}
\descript{\large :\: {Node.js,\, React.js,\, Flask,\, FastAPI,\, GraphQL,\, Mocha,\, Mockito,\, Ethers.js}}

\runsubsection{Technologies}
\descript{\large :\: {Amazon Web Services,\, MongoDB,\, MySQL,\, ElasticSearch,\, Ethereum}}

\sectionsep

\end{document}
